---
title: "Report: Dating a Floating Series"
output: html_document
params:
  fileName1: NA
  fileName2: NA
  floaterObject: NA
  xdParams: NA
  ccfArgs: NA
  floaterSegs: NA
  minOverlap: NA
  excluded: NA
  editDF: NA
  editCode: NA
  datingNotes: NA
  dateLog: NA
  helpers: NA
---

```{r setup, echo=FALSE, message=FALSE}
library(dplR)
library(knitr)
library(kableExtra)
source(params$helpers)
source(file.path(dirname(params$helpers), "plot.floater.R"))
p             <- params$xdParams
ccfArgs       <- params$ccfArgs
excluded      <- params$excluded
floaterObject <- params$floaterObject
fcs           <- floaterObject$floaterCorStats
iBest         <- which.max(fcs$r)
firstBest     <- fcs$first[iBest]
lastBest      <- fcs$last[iBest]
rBest         <- fcs$r[iBest]

fname1 <- if (is.null(params$fileName1)) "Demo Data" else params$fileName1
fname2 <- if (is.null(params$fileName2)) "Demo Data" else params$fileName2
notes  <- if (is.null(params$datingNotes) || params$datingNotes == "") {
  "No dating notes entered."
} else params$datingNotes
flArgs <- c(normArgs, "method")
ed     <- params$editDF
edited <- nrow(ed) > 0
```

### Date: `r Sys.Date()`

### Dated File: `r fname1`

### Undated File: `r fname2`

`r if (edited) paste0("**Edits:** the dated data include ", nrow(ed), " edit(s) made in xDateR, listed in the edit report. The R code below replays them before the analysis.")`

`r if (any(c(fname1, fname2) %in% c("xDateRtest.rwl", "xDateRtestUndated.rwl"))) "The example data are in the data folder of the xDateR repository: https://github.com/OpenDendro/xDateR"`

`r if (length(excluded) > 0) paste0("**Series left out of the master:** ", paste(excluded, collapse = ", "), ".")`

#### Selected Series: `r floaterObject$series.name`

#### Arguments:

```{r,echo=FALSE}
fmt <- function(v) if (is.null(v)) "NULL" else as.character(v)
tab2 <- data.frame(
  Parameter = c("min.overlap", flArgs,
                paste(names(ccfArgs), "(cross-correlation)")),
  Value     = c(params$minOverlap, vapply(p[flArgs], fmt, ""),
                vapply(ccfArgs, fmt, "")))
kable(tab2, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


### Floater Results

Series Name: `r floaterObject$series.name`

Years searched: `r min(fcs$first)` to `r max(fcs$last)`

Highest overall correlation: `r round(rBest, 2)` with dates `r firstBest` to `r lastBest`

`r if (!isTRUE(floaterObject$isBest)) paste0("**Position used: ", floaterObject$first, " to ", floaterObject$last, "**, ", if (is.na(floaterObject$r)) "entered by hand. It could not be checked against the master: there the series overlaps it too little, or not at all, for a correlation." else paste0("chosen by the user (r = ", round(floaterObject$r, 2), "), not the best fit."))`

```{r, echo=FALSE}
plot.floater(floaterObject, params = p)
```

```{r, echo=FALSE}
# computed by dplR; drawn with the app's plotCCF() (dplR's own plot code,
# segments in time order), as on the Floater panel
source(file.path(dirname(params$helpers), "plotCCF.R"))
segs      <- params$floaterSegs
checkable <- !is.null(segs)   # FALSE for a hand-entered position with too little overlap
if (checkable) {
  ccfObject <- suppressMessages(do.call(ccf.series.rwl, c(
    list(rwl = floaterObject$rwlCombined, series = floaterObject$series.name),
    ccfArgs, p[normArgs], list(make.plot = FALSE))))
  plotCCF(ccfObject, pcrit = ccfArgs$pcrit)
}
```

### Candidate positions

```{r, echo=FALSE}
cand <- floaterCandidates(fcs)
kable(data.frame(Years = paste0(cand$first, "-", cand$last), r = round(cand$r, 3),
                 Overlap = cand$n, p = fmtPsmall(cand$p)), row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE, position = "left")
```

`r if (nrow(cand) > 1 && cand$r[1] - cand$r[2] < 0.1) "**Ambiguous:** the two best positions correlate almost equally well."`

`r if (floaterDisagree(fcs)) { st <- floaterStrongest(fcs); paste0("**Check the overlap:** the position with the highest correlation rests on ", fcs$n[which.max(fcs$r)], " years of overlap with the master. ", st$first, "-", st$last, " correlates lower (r = ", round(st$r, 2), ") but over ", st$n, " years, which is stronger evidence (p = ", fmtPsmall(st$p), "). A high correlation over a short overlap is easier to get by chance.") }`

### Segments at the dates used

```{r, echo=FALSE, results="asis"}
if (checkable) {
  f    <- crsFlagged(segs)
  runs <- lagRuns(f, crsTested(segs))
  cat(if (length(runs) == 0) "Every segment fits best where dated (lag search to +/-" else
        paste0(paste(runs, collapse = " "), " (lag search to +/-"),
      segs$lag.max, " years).\n", sep = "")
} else {
  cat("The position used could not be tested segment by segment: the series overlaps the master too little there.\n")
}
```

```{r, echo=FALSE, eval=checkable}
okb <- !is.na(segs$spearman.rho[1, ])
lg  <- segs$best.lag[1, okb]
tab <- data.frame(Segment = sprintf("%g-%g", segs$bins[okb, 1], segs$bins[okb, 2]),
                  r = round(segs$spearman.rho[1, okb], 3),
                  Flag = ifelse(is.na(m <- match(segs$bins[okb, 1], f$from)), "",
                                ifelse(f$weak[m], "B (weak)", f$flag[m])),
                  Lag = ifelse(lg == 0, "", sprintf("%+d", as.integer(lg))),
                  Gain = ifelse(lg == 0, NA, round(segs$best.rho[1, okb] - segs$spearman.rho[1, okb], 3)))
kable(tab, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE, position = "left")
```

### Dating Notes

`r notes`

### Date Log

```{r, echo=FALSE, comment=""}
if (!is.null(params$dateLog)) writeLines(params$dateLog)
```

### R Code

```{r, echo=FALSE, comment=""}
s <- floaterObject$series.name
cat(
  paste(dataCode(fname1, ed, params$editCode), collapse = "\n"), '\n',
  'rwl     <- dat\n',  # the dated master, with any edits
  if (length(excluded) > 0) paste0(
    '# series left out of the master\n',
    'rwl     <- rwl[, setdiff(names(rwl), ', vecCode(excluded), '), drop = FALSE]\n'),
  'undated <- read.rwl("', fname2, '")\n',
  'fo <- xdate.floater(rwl,\n    series = undated[, "', s, '"],\n    series.name = "', s, '",\n    ',
  'min.overlap = ', params$minOverlap, ',\n    ',
  argCode(p, flArgs), ',\n    make.plot = TRUE)\n\n',
  if (isTRUE(floaterObject$isBest)) paste0(
    '# the series at its best-fit dates\n',
    'placed   <- fo$rwlOut\n',
    'combined <- fo$rwlCombined\n\n')
  else paste0(
    '# The position used is not the best fit: the series was placed at ',
    floaterObject$first, '-', floaterObject$last, '\n',
    '# (last year ', floaterObject$last, '), ',
    if (is.na(floaterObject$r)) 'entered by hand' else 'chosen from the candidate positions', '.\n',
    'x <- undated[, "', s, '"]\n',
    'x <- x[!is.na(x)]\n',
    'placed <- as.rwl(data.frame("', s, '" = x, row.names = ', floaterObject$first, ':',
    floaterObject$last, ', check.names = FALSE))\n',
    'combined <- combine.rwl(rwl, placed)\n\n'),
  if (checkable) paste0(
    '# the series segment by segment at those dates, with the lag search\n',
    '# (as.data.frame() keeps every year of the master: taking the column from\n',
    '# the rwl object would trim the years to the series, and corr.rwl.seg()\n',
    '# refuses a series shorter than two segments)\n',
    'segs <- corr.rwl.seg(as.rwl(as.data.frame(combined)["', s, '"]), master = rwl,\n    ',
    argCode(ccfArgs, names(ccfArgs)), ',\n    ',
    argCode(p, c(normArgs, "method", "lag.max")), ',\n    make.plot = FALSE)\n',
    'segs$spearman.rho; segs$best.lag\n\n',
    '# cross-correlations at those dates\n',
    'ccf.series.rwl(combined, series = "', s, '",\n    ',
    argCode(ccfArgs, names(ccfArgs)), ',\n    ',
    argCode(p, normArgs), ',\n    make.plot = TRUE)\n'),
  sep = "")
```
