---
title: "Report: Individual Series Correlations"
output: html_document
params:
  fileName: NA
  floaterObject: NA
  undatedParams: NA
---

```{r,echo=FALSE}
library(DT)
library(knitr)
library(kableExtra)
undatedParams <- params$undatedParams
floaterObject <- params$floaterObject
floaterCorStats <- floaterObject$floaterCorStats
rBest <- which.max(floaterCorStats$r)
firstBest <- floaterCorStats$first[rBest]
lastBest <- floaterCorStats$last[rBest]
rBest <- floaterCorStats$r[rBest]
pBest <- floaterCorStats$p[rBest]

fname <- ifelse(is.null(params$fileName),yes = "Demo Data",no = params$fileName)
```

The original file passed in to the xDateR app was `r fname`. The series selected is `r floaterObject$series.name`. 

###Floater Report
Series Name: `r floaterObject$series.name` 

Years searched `r min(floaterCorStats$first)` to  `r max(floaterCorStats$last)`

Highest overall correlation for series is `round(rBest,2)` with dates `firstBest` to `lastBest`

```{r, echo=FALSE}
 plot.floater(floaterObject)
```

```{r, echo=FALSE}

dat <- floaterObject$rwlCombined
if(undatedParams$n=="NULL"){
  n <- NULL
}
if(undatedParams$n!="NULL"){
  n <- as.numeric(undatedParams$n)
}

ccfObject <- ccf.series.rwl(dat, 
                            series = floaterObject$series.name, 
                            seg.length = undatedParams$seg.length, 
                            bin.floor = as.numeric(undatedParams$bin.floor),
                            n = n,
                            prewhiten = undatedParams$prewhiten, 
                            pcrit = undatedParams$pcrit,
                            biweight = undatedParams$biweight, 
                            method = undatedParams$method,
                            make.plot=TRUE)
```

###Dating Notes

`r undatedParams$datingNotes`
