---
title: "Report: Correlations between Series"
output: html_document
params:
  fileName: NA
  crsObject: NA
  flagged: NA
  xdParams: NA
  excluded: NA
  editDF: NA
  editCode: NA
  helpers: NA
---

```{r setup, echo=FALSE, message=FALSE}
library(dplR)
library(DT)
library(knitr)
library(kableExtra)
source(params$helpers)
crsObject <- params$crsObject
p         <- params$xdParams
excluded  <- params$excluded
fname     <- if (is.null(params$fileName)) "DemoData.rwl" else params$fileName
ed        <- params$editDF
edited    <- nrow(ed) > 0
crsArgs   <- c("seg.length", "bin.floor", normArgs, "pcrit", "method", "lag.max")
```

### Date: `r Sys.Date()`

### File: `r fname`

`r if (edited) paste0("**Edits:** the data analysed here include ", nrow(ed), " edit(s) made in xDateR, listed in the edit report. The R code below replays them before the analysis.")`

`r if (fname %in% c("xDateRtest.rwl", "xDateRtestUndated.rwl")) "The example data are in the data folder of the xDateR repository: https://github.com/OpenDendro/xDateR"`

`r if (length(excluded) > 0) paste0("**Series left out of the master:** ", paste(excluded, collapse = ", "), ".")`

#### Arguments:

```{r,echo=FALSE}
fmt <- function(v) if (is.null(v)) "NULL" else as.character(v)
tab1 <- data.frame(Parameter = crsArgs,
                   Value     = vapply(p[crsArgs], fmt, ""))
kable(tab1, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


```{r,echo=FALSE, fig.width=10, fig.height=8}
plot(crsObject)
```


<div style = "width:80%; height:auto; margin: auto;">
```{r,echo=FALSE}
res <- data.frame(Series = rownames(crsObject$overall),
                  Correlation = round(crsObject$overall[, 1], 3),
                  p = fmtP(crsObject$overall[, 2]),
                  pnum = crsObject$overall[, 2],
                  stringsAsFactors = FALSE)
datatable(res,rownames = FALSE,
          caption = "Overall Series Correlation (shaded: not significant at P crit)",
          autoHideNavigation=TRUE,
          options = list(pageLength = nrow(res),
                         searching=FALSE,
                         lengthChange=FALSE,
                         columnDefs = list(
                           list(visible = FALSE, targets = 3),
                           list(orderData = 3, className = 'dt-right', targets = 2)))) %>%
  formatStyle('pnum', target = 'row',
              backgroundColor = styleInterval(crsObject$pcrit - 1e-12,
                                              c('transparent', '#fde4e4')))
```


```{r,echo=FALSE}
    binNames <- paste(crsObject$bins[,1], "-", crsObject$bins[,2], sep="")
    res <- data.frame(series=binNames,round(crsObject$avg.seg.rho,3))
    colnames(res) <- c("Bin","Correlation")
    res <- res[!is.na(res$Correlation), ]
    datatable(res,rownames = FALSE,
              caption = "Avg. Correlation by Bin",
              autoHideNavigation=TRUE,
              options = list(pageLength = min(30,nrow(res)),
                             searching=FALSE,
                             lengthChange=FALSE))
```

```{r,echo=FALSE}
f <- params$flagged
noFlags <- is.null(f) || nrow(f) == 0
```
</div>

`r if (noFlags) "There are no flagged segments."`

`r if (!noFlags) "#### Flagged Segments"`

`r if (!noFlags) paste0("A: correlation under pcrit, but best where dated. B: correlates better at another lag (searched to ±", crsObject$lag.max, " years); a negative lag suggests missing rings, a positive lag false rings. A weak B is under the critical value even at its best lag.")`

```{r,echo=FALSE}
if (!noFlags) {
  flagsDF <- data.frame(Series  = f$series,
                        Segment = paste0(f$from, "-", f$to),
                        Flag    = ifelse(f$weak, "B (weak)", f$flag),
                        r       = round(f$r.dated, 3),
                        Lag     = ifelse(f$flag == "B", sprintf("%+d", as.integer(f$best.lag)), ""),
                        r.lag   = round(f$r.lag, 3),
                        Gain    = round(f$gain, 3))
  kable(flagsDF, row.names = FALSE) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
}
```

```{r,echo=FALSE}
    binNames <- paste(crsObject$bins[,1], "-", crsObject$bins[,2], sep="")
    rho <- round(crsObject$spearman.rho,3)
    flag <- ifelse(crsObject$best.lag != 0, "B",
                   ifelse(crsObject$p.val >= crsObject$pcrit, "A", ""))
    flag[is.na(flag)] <- ""
    nb <- ncol(rho)
    res <- data.frame(Series = rownames(rho), rho, flag, check.names = FALSE,
                      stringsAsFactors = FALSE)
    colnames(res) <- c("Series", binNames, paste0("flag", seq_len(nb)))
    datatable(res,rownames = FALSE,
              caption = "Series Correlation by Bin (red: A, under the critical value but best where dated; purple: B, fits better at another lag)",
              autoHideNavigation=TRUE,
              options = list(pageLength = min(30,nrow(res)),
                             searching=TRUE,
                             lengthChange=FALSE,
                             scrollX=TRUE,
                             columnDefs = list(list(visible = FALSE,
                                                    targets = nb + seq_len(nb))))) %>%
      formatStyle(columns = binNames, valueColumns = paste0("flag", seq_len(nb)),
                  backgroundColor = styleEqual(c("A", "B"), c("#fde4e4", "#ead9f5")))
```


### R Code
```{r, echo=FALSE, comment=""}
cat(
  paste(dataCode(fname, ed, params$editCode), collapse = "\n"), '\n\n',
  if (length(excluded) > 0) paste0(
    '# series left out of the master\n',
    'dat <- dat[, setdiff(names(dat), ', vecCode(excluded), '), drop = FALSE]\n'),
  'crs <- corr.rwl.seg(dat,\n    ', argCode(p, crsArgs), ',\n    make.plot = TRUE)\n',
  '# data in the tables above are available in the\n',
  '# crs object via the list elements. e.g.\n',
  'str(crs)\n',
  'crs$overall\n', sep = "")
```
