---
title: "Report: Edits Log"
output: html_document
params:
  fileName: NA
  editLog: NA
  editDF: NA
  editCode: NA
  helpers: NA
---

```{r setup, echo=FALSE}
fname <- if (is.null(params$fileName)) "DemoData.rwl" else params$fileName
ed    <- params$editDF
```

### Date: `r Sys.Date()`

### File: `r fname`


### Log
```{r, echo=FALSE, comment=""}
writeLines(params$editLog)
```

### R Code

The edits below use two small functions, `editRing()` and `fillGaps()`, that
xDateR itself uses. They wrap dplR's `insert.ring()`, `delete.ring()` and
`fill.internal.NA()` so that each edit changes only the series' own span and
keeps the years of any gaps correct. Run the definitions first, then the edits
in order: each edit's year refers to the data after the edits before it.
As in dplR, `delete` removes the ring at `year` and `insert` adds the new
ring after `year`.

```{r, echo=FALSE, comment=""}
source(params$helpers)
writeLines(userCode(params$editCode))
```

```{r, echo=FALSE, comment=""}
source(params$helpers)
writeLines(c("library(dplR)",
             paste0('dat <- read.rwl("', fname, '")'),
             editStepsCode(ed)))
```
