---
title: "Report: Individual Series Correlations"
output: html_document
params:
  fileName: NA
  series: NA
  seriesFull: NA
  plotCode: NA
  xdParams: NA
  excluded: NA
  lagCCF: NA
  winCCF: NA
  datingNotes: NA
  editDF: NA
  editCode: NA
  helpers: NA
---

```{r setup, echo=FALSE, message=FALSE}
library(dplR)
library(knitr)
library(kableExtra)
source(params$helpers)
p        <- params$xdParams
excluded <- params$excluded
fname    <- if (is.null(params$fileName)) "DemoData.rwl" else params$fileName
notes    <- if (is.null(params$datingNotes) || params$datingNotes == "") {
  "No dating notes entered."
} else params$datingNotes
ed       <- params$editDF
edited   <- nrow(ed) > 0
cssArgs  <- c("seg.length", "bin.floor", normArgs, "pcrit", "method")
ccfArgs  <- c("seg.length", "bin.floor", normArgs, "pcrit")
```

### Date: `r Sys.Date()`

### File: `r fname`

`r if (edited) paste0("**Edits:** the data analysed here include ", nrow(ed), " edit(s) made in xDateR, listed in the edit report. The R code below replays them before the analysis.")`

`r if (fname %in% c("xDateRtest.rwl", "xDateRtestUndated.rwl")) "The example data are in the data folder of the xDateR repository: https://github.com/OpenDendro/xDateR"`

#### Selected Series:

**`r params$series`**

`r if (params$series %in% excluded) "This series is left out of the master and is tested against the master built from the others."`

#### Series in Master:

```{r,echo=FALSE}
nms <- colnames(params$seriesFull$rwl)
i <- 4
j <- ceiling(length(nms) / i)
res <- matrix(c(nms, rep("", i * j - length(nms))), nrow = j, ncol = i)
res2 <- kable(res, format="html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
gsub("<thead>.*</thead>", "", res2)
```

#### Arguments:

```{r,echo=FALSE}
fmt <- function(v) if (is.null(v)) "NULL" else as.character(v)
tab2 <- data.frame(Parameter = c(cssArgs, "lag.max"),
                   Value     = c(vapply(p[cssArgs], fmt, ""), params$lagCCF))
kable(tab2, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


```{r, echo=FALSE, fig.width=10, fig.height=8}
css <- do.call(corr.series.seg, c(params$seriesFull, p[cssArgs],
                                  list(make.plot = TRUE)))
```


```{r, echo=FALSE, fig.width=10, fig.height=8}
# the whole series is analysed; only the segments inside the chosen years
# are drawn (plotCCF(), printed in the R code below)
eval(parse(text = params$plotCode))
ccfObject <- suppressMessages(do.call(ccf.series.rwl,
                                      c(params$seriesFull, p[ccfArgs],
                                        list(lag.max = params$lagCCF,
                                             make.plot = FALSE))))
plotCCF(ccfObject, from = params$winCCF[1], to = params$winCCF[2], pcrit = p$pcrit)
```


### Dating Notes
`r notes`

### R Code

```{r, echo=FALSE, comment=""}
s <- params$series
cat(
  paste(dataCode(fname, ed, params$editCode), collapse = "\n"), '\n\n',
  '# the master: every series except "', s, '"',
  if (length(excluded) > 0) ' and those left out of the master', '\n',
  'master <- dat[, setdiff(names(dat), ', vecCode(unique(c(s, excluded))), '), drop = FALSE]\n',
  'series <- setNames(dat[["', s, '"]], rownames(dat))\n',
  'css <- corr.series.seg(master, series = series,\n    ',
  argCode(p, cssArgs), ',\n    make.plot = TRUE)\n\n',
  '# cross-correlations by segment, on the whole series\n',
  'ccfObject <- ccf.series.rwl(master, series = series,\n    ',
  argCode(p, ccfArgs), ',\n    lag.max = ', params$lagCCF, ',\n    make.plot = FALSE)\n\n',
  '# the plot above shows the segments inside ', params$winCCF[1], '-', params$winCCF[2],
  '.\n# ccf.series.rwl() draws every segment, so this function draws the chosen ones\n',
  '# (it is dplR\'s own plotting code):\n',
  paste(userCode(params$plotCode), collapse = "\n"), '\n\n',
  'plotCCF(ccfObject, from = ', params$winCCF[1], ', to = ', params$winCCF[2],
  ', pcrit = ', p$pcrit, ')\n',
  sep = "")
```
