---
title: "Report: Data Overview"
output: html_document
params:
  fileName: NA
  rwlObject: NA
  rwlPlotType: NA
  editDF: NA
  editLog: NA
  editCode: NA
  checks: NA
  rwlReport: NA
  helpers: NA
---

```{r setup, echo=FALSE, message=FALSE}
library(dplR)
library(knitr)
library(kableExtra)
source(params$helpers)
dat    <- params$rwlObject
ed     <- params$editDF
fname  <- params$fileName
edited <- nrow(ed) > 0
chk    <- params$checks
gaps   <- rwlGaps(dat)
ks <- function(x) kable_styling(x, bootstrap_options = c("striped", "hover", "condensed"),
                                full_width = FALSE, position = "left")
```

### Date: `r Sys.Date()`

### File: `r fname`

Made with xDateR using dplR `r packageVersion("dplR")`. The R code at the end
reproduces everything in this report.

`r if (fname == "xDateRtest.rwl") "The example data are in the data folder of the xDateR repository: https://github.com/OpenDendro/xDateR"`

`r if (edited) "### Edits applied"`

`r if (edited) paste0("This report describes the data after ", nrow(ed), " edit(s) made in xDateR, listed below in the order they were made. The R code replays them.")`

```{r, echo=FALSE, comment=""}
if (edited) writeLines(params$editLog)
```

### Data summary

```{r, echo=FALSE, comment=""}
# the app's rwl.report(dat), passed in rather than recomputed: on a large
# file it takes over a minute
print(params$rwlReport)
```

`r if (nrow(gaps) > 0) "### Gaps (years with no measurement)"`

`r if (nrow(gaps) > 0) "dplR reads these as missing, not as zero-width rings. Correlations skip them; the skeleton plot cannot be drawn across them; the spline filter (nyrs) stops on them."`

```{r, echo=FALSE}
if (nrow(gaps) > 0) {
  kable(data.frame(Series = gaps$series, Years = formatGaps(gaps), check.names = FALSE),
        row.names = FALSE) %>% ks()
}
```

### Data checks

```{r, echo=FALSE, results="asis"}
if (nrow(chk) == 0) {
  cat("`rwl.check()` found nothing to flag.\n")
} else {
  n <- table(factor(chk$severity, levels = c("error", "warning", "note")))
  cat(sprintf("`rwl.check()` found %d error(s), %d warning(s) and %d note(s).\n\n",
              n[["error"]], n[["warning"]], n[["note"]]))
}
```

```{r, echo=FALSE}
serious <- chk[chk$severity %in% c("error", "warning"), ]
if (nrow(serious) > 0) {
  yrs <- ifelse(is.na(serious$year.from), "",
                ifelse(is.na(serious$year.to) | serious$year.from == serious$year.to,
                       serious$year.from, paste0(serious$year.from, "-", serious$year.to)))
  kable(data.frame(Severity = serious$severity, Check = serious$check,
                   Series = ifelse(is.na(serious$series), "", serious$series),
                   Years = yrs, Finding = serious$message),
        row.names = FALSE) %>% ks()
}
```

```{r, echo=FALSE}
notes <- chk[chk$severity == "note", ]
if (nrow(notes) > 0) {
  agg <- do.call(rbind, lapply(split(notes, notes$check), function(x) {
    data.frame(Check = x$check[1], Findings = nrow(x),
               Series = if (all(is.na(x$series))) "" else
                 paste(sort(unique(x$series[!is.na(x$series)])), collapse = ", "))
  }))
  kable(agg, row.names = FALSE, caption = "Notes, one row per kind") %>% ks()
}
```

### Plot

```{r, echo=FALSE, fig.width=10, fig.height=8}
plot(dat, plot.type = params$rwlPlotType)
```

### Series

```{r, echo=FALSE}
kable(summary(dat), row.names = FALSE, digits = 3) %>% ks()
```

### R Code

```{r, echo=FALSE, comment=""}
writeLines(c(dataCode(fname, ed, params$editCode), "",
             "rwl.report(dat)",
             paste0('chk <- rwl.check(dat, file = "', fname, '")'),
             "as.data.frame(chk)",
             paste0('plot(dat, plot.type = "', params$rwlPlotType, '")'),
             "summary(dat)"))
```
