---
title: "Report: Individual Series Correlations"
output: html_document
params:
  fileName1: NA
  fileName2: NA
  floaterObject: NA
  undatedParams: NA
---

```{r,echo=FALSE}
library(DT)
library(knitr)
library(kableExtra)
undatedParams <- params$undatedParams
floaterObject <- params$floaterObject
floaterCorStats <- floaterObject$floaterCorStats
rBest <- which.max(floaterCorStats$r)
firstBest <- floaterCorStats$first[rBest]
lastBest <- floaterCorStats$last[rBest]
rBest <- floaterCorStats$r[rBest]
pBest <- floaterCorStats$p[rBest]

fname1 <- ifelse(is.null(params$fileName1),yes = "Demo Data",no = params$fileName1)
fname2 <- ifelse(is.null(params$fileName2),yes = "Demo Data",no = params$fileName2)
```

### Date: `r Sys.Date()`

### Dated File: `r fname1`

### Undated File: `r fname2`

#### Selected Series: `r floaterObject$series.name`

#### Arguments:

```{r,echo=FALSE}
tab2 <- data.frame(Parameter=c("seg.length","bin.floor","n",
                               "prewhiten","pcrit","biweight",
                               "method"),
                   Value=c(undatedParams$seg.length,
                           undatedParams$bin.floor,
                           undatedParams$n, 
                           undatedParams$prewhiten, 
                           undatedParams$pcrit, 
                           undatedParams$biweight,
                           undatedParams$method))
kable(tab2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


###Floater Report
Series Name: `r floaterObject$series.name` 

Years searched `r min(floaterCorStats$first)` to  `r max(floaterCorStats$last)`

Highest overall correlation for series is `round(rBest,2)` with dates `firstBest` to `lastBest`

```{r, echo=FALSE}
 plot.floater(floaterObject)
```

```{r, echo=FALSE}

dat <- floaterObject$rwlCombined
if(undatedParams$n=="NULL"){
  n <- NULL
}
if(undatedParams$n!="NULL"){
  n <- as.numeric(undatedParams$n)
}

ccfObject <- ccf.series.rwl(dat, 
                            series = floaterObject$series.name, 
                            seg.length = undatedParams$seg.length, 
                            bin.floor = as.numeric(undatedParams$bin.floor),
                            n = n,
                            prewhiten = undatedParams$prewhiten, 
                            pcrit = undatedParams$pcrit,
                            biweight = undatedParams$biweight, 
                            method = undatedParams$method,
                            make.plot=TRUE)
```

###Dating Notes

`r undatedParams$datingNotes`

###R Code

Reproducible R code is not available yet. The crossdating function `xdate.floater` will be included in the next `dplR` release.
